author_name

### 2021-03-03 inst/examples/author_name.Rmd
change

>>>>

## Authors

* `r length(unique(df$author_name))` [unique authors](output.tables/author_accepted.csv) These final names capture all name variants from the custom [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv), and exclude known pseudonymes (see below). If multiple names for the same author are still observed on this list, they should be added on the [author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv).
 * `r sum(!is.na(df$author_name))` documents have unambiguous author information (`r round(100*mean(!is.na(df$author_name)))`%). 
 * `r length(readLines(paste0(getwd(),"/output.tables/pseudonyme_accepted.csv")))` [unique pseudonymes](output.tables/pseudonyme_accepted.csv) are recognized based on [custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv).
 * `r length(readLines(paste0(getwd(),"/output.tables/author_discarded.csv")))-2` [discarded author names](output.tables/author_discarded.csv) This list should not include any real authors (if it does, please send a note to the admin). The stopword lists are considered when discarding names.
 * [Author name conversions](output.tables/author_conversion_nontrivial.csv) Non-trivial conversions from the original raw data to final names.

### Auxiliary files

 * [Author synonyme table](https://github.com/COMHIS/fennica/blob/master/inst/extdata/ambiguous-authors.csv)
 * [Stopwords for names](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_for_names.csv)
 * [Stopwords for titles](https://github.com/COMHIS/fennica/blob/master/inst/extdata/stopwords_titles.csv)
 * [Custom pseudonyme lists](https://github.com/COMHIS/fennica/blob/master/inst/extdata/names/pseudonymes/custom_pseudonymes.csv)

Top-`r ntop` uniquely identified authors and their productivity (title count).

```{r summaryauthorsnames, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, out.width='430px', fig.show='hold'}
knitr::opts_chunk$set(fig.path = "figure/", dev="CairoPNG")
theme_set(theme_bw(base_size = 12))
p <- NULL
p <- top_plot(df, "author_name", ntop) +
     		  ggtitle(paste("Top authors' names")) +
		  ylab("Documents")
print(p)
```

### Author productivity

Title count versus paper consumption (all authors):

```{r authortitlespapers, fig.height=8, fig.width=18, echo=FALSE, warning=FALSE}
theme_set(theme_bw(base_size = 12))
res1 <- compare_title_paper(df, "author_name", plot.mode = "text")
res2 <- compare_title_paper(df, "author_name", plot.mode = "point")
grid.arrange(res2$plot, res1$plot, nrow = 1)
#kable(res1$table)
```
